Failure Behaviour Analysis of Automated Pond Oxygen Management System

### 2015-02-19 IFIP FTA/manuscript.tex
go go gfofofofof

FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems. Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on. FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.  Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}. \textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
Elctornics system has used the FTA to study the behaviour of electronics system. Authors in [Microelectronics Reliability] uses FTA on printed circuit board assembly and 
for assessment of power system reliability [Reliability Engineering  System Safety]. The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  [Biological Invasions].} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.

>>>>

FTA has been widely used in different areas to perform both qualitative and quantitative dependability analysis of the systems. Systems that have been analysed using FTA include but not limited to propulsion systems on spacecraft, braking systems in cars, Nuclear Power Plants, and so on. FTA has been used to analyse the reliability of the power system in  \cite{volkanovski2009,cepin2011assessment}, power supply system to railways in  \cite{Chen2007}, and cogeneration power plant in textile mill in \cite{Ramesh2011}.  Recently, fault tree analysis has been applied on Clinical workflows to ensure the safety of these high-risk workflows \cite{lamis2014} and it is also used to prevent wrong-side surgery to patients \cite{abecassis2015}. \textbf{The fault tree for pressure tank analysis has been proposed in [NASA Office of Safety and Mission Assurance].
Elctornics system has used the FTA to study the behaviour of electronics system. Authors in \cite{shu2006using} uses FTA on printed circuit board assembly and 
for assessment of power system reliability [Reliability Engineering  System Safety]. The biological system uses the FTA to analysis the failure of biomedical operation such as Analysis for Biological Invasions  \cite{hayes2002identifying}.} Different tools like HiP-HOPS\cite{Papadopoulos2012}, Reliability Workbench\cite{Isograph2014}  are available to perform fault tree analysis.
